A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-31 4_method.tex
lil formula updates

We also filter unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
If the upper node has the same bead count $B^*_{v_0} = B^*_{v_1}$ we mark all bones and nodes $v$ in between, and set the bead count $B^*_v \leftarrow B^*_{v_0}$.

@@

For each marked bone between $v_0$ and $v_1$ with $v_0.B^* \neq v_1.B*$ we introduce transitions.
A transition from bead count $n$ to $n+1$ will be placed anchored on each location $v_x$ where $R(v_x) = b^{-1}(n)$.
We can compute the location of the anchor simply as
$$v_x = v_0 + (v_1 - v_0) (b^{-1}(n) - R(v_0)) / (R(v_1) - R(v_0))$$
for each $n$ such that $v_0.B^*<n<v_1.B^*$.
See \cref{beading_transitioning_filtering__transition_mids}.

A transition with length $t(n)$ will be placed somewhere covering the anchor position.
We determine the distance between the anchor $v$ and the lower transition end $v_0$ proportial to the positioning of the transition relative to the preferred distances: 
$$d_-^\text{transition}(v) =  t(n) (b^{-1}(n) - p(n) ) / (p(n+1) - p(n))$$
%See \cref{transition_placement}.
For the other end we have $d_+^\text{transition}(v) = t(n) - d_-^\text{transition}(v)$.
That way the transitions never overlap locations with preferred bead count.

>>>>

We also filter unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
If the upper node has the same bead count $B^*_{v_1} = B^*_{v_0}$ we mark all bones and nodes $v$ in between, and set the bead count $B^*_v \leftarrow B^*_{v_0}$.

@@

For each marked bone between $v_0$ and $v_1$ with $v_0.B^* \neq v_1.B*$ we introduce transitions.
A transition from bead count $n$ to $n+1$ will be placed anchored on each location $v_x$ where $R(v_x) = b^{-1}(n)$.
We can compute the location of the anchor simply as
$$v_x = v_0 + (v_1 - v_0) \frac{ b^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
for each $n$ such that $v_0.B^*<n<v_1.B^*$.
See \cref{beading_transitioning_filtering__transition_mids}.

A transition with length $t(n)$ will be placed somewhere covering the anchor position.
We determine the distance between the anchor $v$ and the lower transition end $v_0$ proportial to the positioning of the transition relative to the preferred distances: 
$$d_-^\text{transition}(v) =  t(n) \frac{ b^{-1}(n) - p(n) }{ p(n+1) - p(n) }$$
%See \cref{transition_placement}.
For the other end we have $d_+^\text{transition}(v) = t(n) - d_-^\text{transition}(v)$.
That way the transitions never overlap locations with preferred bead count.
\todo{TODO: introduce $p$ first!}
